\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\date{}

\begin{document}

\begin{longtable}[]{@{}lllll@{}}
\toprule
Reference & Research Purpose & Research Methods & Results &
Challenges/Research Gaps\tabularnewline
\midrule
\endhead
1 & Multilingual Hate Speech Detection & BERT & 83\% & Wrong
classification due to annotation's dilemma (AD), Wrong classification
due to confounding factors (CF), Wrong classification due to hidden
context (HC)\tabularnewline
2 & Bengali Hate Speech Detection & BERT & 97\% & Limited
dataset\tabularnewline
3 & Multilingual Hate Speech Detection & BERT & 89\% in English,

87\% in malay. & Limited range of hyperparameters of

the BERT models\tabularnewline
4 & Multi-label hate speech detection & DistilBERT & 80.36\% & Shortage
of collected data\tabularnewline
5 & Cross-Lingual Few-Shot Hate Speech and Offensive Language Detection
& Proto-MAML & 63.1\% & Shortage of collected data\tabularnewline
6 & Hate Speech detection in the Bengali language:

A dataset and its baseline evaluation & SVM & 87.5\% & The lack of
sufficient data.\tabularnewline
7 & Hate speech detection: Challenges and

solutions & BERT,Multi-view SVM & 82.01\% & Need for more research on
technical and practical matters.\tabularnewline
8 & hate speech detection on social

media using neural network & Recurrent neural network (RNN),CNN & 77\% &
The lack of sufficient data.Further,need more datasets.\tabularnewline
9 & Hate Speech and Offensive Language Detection in Bengali &
m-BERT,XLM-Roberta,IndicBERT,muRIL,ELFI & 83\% & only analyzed publicly
available data crawled

via Twitter API.\tabularnewline
10 & SOCIAL MEDIA

COMMENTS FOR HATE SPEECH DETECTION IN BANGLA & BERT & 86.78\% & Found
that emoji and punctuation do not affect HS detection\tabularnewline
11 & Multilingual Racial Hate Speech Detection Using Transfer Learning &
BERT and HateXplain & 88\%

F1-score 86\% & Due to the limitation of time they were unable to
research further.\tabularnewline
12 & Automated Sentiment and Hate Speech Analysis of Facebook

Data by Employing Multilingual Transformer Models. & XLM-T and NLP &
F1-score

Hateful

71\%

Non-hateful 83\% & Hateful Speech detection Precision is only
55\%\tabularnewline
13 & Large Annotated Dataset for Multi-Domain

and Multilingual Hate Speech Identification. & BERT-Zero Shot & 93\% &
Cannot detect leetspeak\tabularnewline
14 & Combating Hate: How Multilingual

Transformers Can Help Detect Topical Hate Speech. & LASER + SVM

Baseline,

mBERT and XLM-RoBERTA & Lowest 68.2\% and highest 85\% & Smaller
datasets with class imbalance produced a weak fit.\tabularnewline
15 & LMU at HaSpeeDe3: Multi-Dataset Training for Cross-Domain Hate
Speech Detection. & AlBERTo, UmBERTo, mBERT and XML-R & Around 64\% &
The accuracy is not that great. More data required.\tabularnewline
16 & Hate Speech Detection in Italian Social Media Text & XML-Base,
XLM-Large,

mBERT, ITA-Base-XXL & 88.63\% & Limited evaluation of hate speech
detection models on Italian language subset.\tabularnewline
17 & Multi-Task Learning Approach to Hate Speech

Detection & BERT,BETO & 86.58\%. & Limited focus on improving dataset
quality for enhanced model learning.\tabularnewline
18 & BERT-Mini Model for Hate-Speech Detection & BERT & 98.6\% & Does
not thoroughly investigate how to optimize the BERT model for better
performance.\tabularnewline
19 & Emotionally Informed Hate Speech Detection & ELMo,

CNN\textbf{FastText},

BERT & 91.3\% & The research does not fully consider how the meaning of
words and context affects accurately identifying hate
speech.\tabularnewline
20 & Hate Speech Detection Using

Natural Language Processing Techniques & CNN & 91\% & Limited
dataset\tabularnewline
21 & Political and

Religious Hate Speech Detection & BERT & 91\% & Out-of-domain setting
does not work properly.\tabularnewline
22 & Hate

Speech & BERT,G-BERT & 95.56\% & Multiple language sentences are
included in the Dataset. Some languages have less data .\tabularnewline
23 & Bengali Hate Speech Detection & BERT & 80\% & Shortage of collected
data\tabularnewline
24 & Contextual Information

in Hate Speech Detection & BERT & 61.3\% & we can observe that the
dataset has complex,limited dataset, long contexts.\tabularnewline
25 & Bangla hate speech & G-BERT & 95.56\% & Banglish sentence is not
included\tabularnewline
\bottomrule
\end{longtable}

\end{document}
